\documentclass[10pt, a4paper]{memoir}
\usepackage{graphicx} % SO I CAN DO TWO IMAGES IN ONE PLACE HEHE
\usepackage{subcaption} % SEE ABOVE
\usepackage{hyperref} % EVERYTHING IS LINKED TO EVERYTHING ELSE ISN'T IT GREAT
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{amssymb}
\graphicspath{ {./src/}} % LOCATION OF IMAGES

\title{Quantum Technology I, Lecture Notes}
\date{WS20/21}



% SO ANGSTROM IS NOT TAKING SO LONG TO TYPE I AM LAZY
\newcommand{\angstrom}{\textup{\AA}}

% FOR THE QUOTES
\epigraphfontsize{\small\itshape}
\setlength\epigraphwidth{10cm}
\setlength\epigraphrule{0pt}


\newenvironment{myitemize} % list then do not look so big and dumb
{ \begin{itemize}
    \setlength{\itemsep}{0pt}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0pt}     }
{ \end{itemize}                  }


\settypeblocksize{0.8\stockheight}{0.7\stockwidth}{*}
\setlrmargins{*}{*}{1.2}
\setulmargins{*}{*}{1.4}
\checkandfixthelayout[nearest]

\begin{document}

\maketitle
\frontmatter
\tableofcontents*


\mainmatter
\include{introduction}
\include{ionsources}
\include{particleaccelerators}
\include{transport}
\include{beamparameters}
\include{basicsofinteraction}
\include{interaction2}
\include{ionrange}
\include{channeling}
\include{beammethods}
\include{ionbeamsinsemiconductor}

\begin{thebibliography}{9}

\bibitem{1}
Harold Patterson Mahon.
\textit{Design of an electrostatic deflector for the ion beam of the Oregon State College cyclotron}.
Oregon State University, 1954.

\bibitem{2}
Richard Rhodes
\textit{The Making of the Atomic Bomb}
Simon and Schuster, 1986

\bibitem{3}
J. F. Ziegler, J. P. Biersack, and U. Littmark.
\textit{The stopping and range of ions in solids},
The stopping and ranges of ions in matter, vol 1,
Pergamon Press, New York, New York, 1985.

\bibitem{4}
University of Helsinki.
\textit{Notes on Plasma Physics}.
\href{http://beam.helsinki.fi/~knordlun/mdh/rangetext.html}{online}.

\bibitem{5}
Vittone Ettore.
\textit{Semiconductor Characterization by Scanning Ion Beam Induced Charge (IBIC) Microscopy}.
International Scholarly Research Notices, 2013.
\href{https://doi.org/10.1155/2013/637608}{doi}

\bibitem{chen}
Francis F. Chen.
\textit{Introduction to Plasma Physics},
Plenum Publishing, New York, New York, 1977

\end{thebibliography}

\end{document}